### 2013-09-05 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
whiitespace tweaks
updating dissertation doc build

For a multiple set analysis of the weak scaling timing results, we
again have to consider that adding sets to the problem is actually a
form of strong scaling. Consider a single set problem ($S=1$) for a
given $P$ and $N$. When that problem is now solved using 2 sets we
have $S=2$, $N$, and $2P$. For any number of sets we then have a
global problem size of $N$ while the number of processors is $SP$
where $P$ is the number of processors in the single set
case. Therefore, $N/P$ is no longer fixed in the weak scaling study
but rather $N/(SP)$ is fixed. As a result, we modify the weak scaling
absolute efficiency relationship to account for this fact:
\begin{equation}
\eta_{weak}(M|N,P|Q,S) = \frac{T(M,Q)}{S \times T(N,P)}\:,
  \label{eq:ms_weak_efficiency}
\end{equation}
where now the absolute efficiency is a function of the number of sets
in the problem and again $M/Q = N/P$. As with the strong scaling
study, we will use the 16-core single set case as the reference
computation for efficiencies. Interestingly,
Eq~(\ref{eq:ms_weak_efficiency}) has a very similar form to the strong
scaling efficiency given by Eq~(\ref{eq:strong_scaling_absolute}),
representative of the strong scaling nature of adding additional
sets. For problems where adding sets improves time to solution, this
new weak scaling formulation accounts for how efficiently those extra
resources are incorporated into the problem.

>>>>

For a multiple set analysis of the weak scaling timing results, we
again have to consider that adding sets to the problem is actually a
form of strong scaling. Consider a single set problem ($S=1$) for a
given $P$ and $N$. When that problem is now solved using 2 sets we
have $S=2$, $N$, and $2P_s$ where $P_s$ is the number of processors in
a single set. For any number of sets we then have a global problem
size of $N$ while the number of processors is $SP_s$. Therefore, $N/P$
is no longer fixed in the weak scaling study but rather $N/(SP_s)$ is
fixed. As a result, we modify the weak scaling absolute efficiency
relationship to account for this fact:
\begin{equation}
\eta_{weak}(M|N,P|Q,S) = \frac{T(M,Q)}{S \times T(N,P)}\:,
  \label{eq:ms_weak_efficiency}
\end{equation}
where now the absolute efficiency is a function of the number of sets
in the problem and again $M/Q = N/P$. As with the strong scaling
study, we will use the 16-core single set case as the reference
computation for efficiencies. Interestingly,
Eq~(\ref{eq:ms_weak_efficiency}) has a very similar form to the strong
scaling efficiency given by Eq~(\ref{eq:strong_scaling_absolute}),
representative of the strong scaling nature of adding additional
sets. For problems where adding sets improves time to solution, this
new weak scaling formulation accounts for how efficiently those extra
resources are incorporated into the problem.
